High resolution, annual maps of field boundaries for  smallholder-dominated croplands at national scales

### 2021-10-16 inst/manuscript/manuscript.Rmd
Frontiers second revision

The detail, temporal precision, and large extent of our maps was enabled by our use of PlanetScope data, which is currently the only source of sub-5 meter imagery with daily coverage [@McCabefutureEarthobservation2017]. These spatial-temporal characteristics, together with the compositing technique we developed, allowed us to develop a complete image catalog for Ghana covering the two major seasons in the 2018 agricultural year. Daily revisits were key to this capability, as they increased the number of cloud-free observations that could be collected in each season. Over rainy tropical regions, such as southern Ghana, the odds of obtaining a single clear PlanetScope observation within a 1-2 week period is often less than 50% [@royGlobalAnalysisTemporal2021]. Although Sentinel-2 is free and has sufficient spatial resolution to effectively classify small-scale croplands [e.g. @Defournyrealtimeagriculturemonitoring2019; @kernerRapidResponseCrop2020], its 5-day interval is likely too infrequent to generate adequate seasonal composites over much of Ghana. The smaller number of clear observations that Sentinel-2 can provide compared to a daily acquisition schedule would result in greater reflectance discontinuities and residual cloud cover in the resulting composites. Given Ghana's persistent cloudiness, such artifacts were present in a number of our PlanetScope composites. However, these were not large enough to have an appreciable impact on the resulting maps, as the mapping algorithms appeared to be relatively insensitive to these anomalies and any discontinuities along tile boundaries.

@@

## Broader applications
This work demonstrates a proof of concept for developing high resolution, annual maps of smallholder-dominated croplands at national to regional scales, using an approach that follows recommended best practices for training and assessing machine learning models [@ElmesAccountingtrainingdata2020]. This approach can be readily updated to integrate improvements, such as newer machine learning models. Beyond providing valuable insights into field characteristics, field boundary maps can help improve remote estimation of crop areas and yield [e.g. @EstesProjectedclimateimpacts2013], and provide deeper insights into important socioeconomic aspects of agricultural systems, such as the relationships between agricultural productivity and farm size [@CarlettoFactartifactimpact2013; @desiereLandProductivityPlot2018; @federRelationFarmSize1985]. Such maps will be important for understanding the rapid agricultural change that is currently occurring in Africa.

## Data availability and usage
The maps presented here are a version 1 product that is freely available to use, along with its underlying code (see SI). In their current form, they may be useful for a variety of research applications. For example, analyzing the distributions of values in the probability maps may provide additional insight into the relative extents of active versus fallow croplands [@Tongforgottenlanduse2020]. However, use of these data for inventory estimates, to develop other map products, or to guide decision-making should be made with caution and account for the reported errors [@OlofssonGoodpracticesestimating2014; @StehmanKeyissuesrigorous2019; @Esteslargeareaspatiallycontinuous2018].

>>>>

The detail, temporal precision, and large extent of our maps was enabled by our use of PlanetScope data, which is currently the only source of sub-5 meter imagery with daily coverage [@McCabefutureEarthobservation2017]. These spatial-temporal characteristics, together with the compositing technique we developed, allowed us to create a complete image catalog for Ghana covering the two major seasons in the 2018 agricultural year. Daily revisits were key to this capability, as they increased the number of cloud-free observations that could be collected in each season. Over rainy tropical regions, such as southern Ghana, the odds of obtaining a single clear PlanetScope observation within a 1-2 week period is often less than 50% [@royGlobalAnalysisTemporal2021]. Although Sentinel-2 is free and has sufficient spatial resolution to effectively classify small-scale croplands [e.g. @Defournyrealtimeagriculturemonitoring2019; @kernerRapidResponseCrop2020], its 5-day interval is likely too infrequent to generate adequate seasonal composites over much of Ghana. The smaller number of clear observations that Sentinel-2 can provide compared to a daily acquisition schedule would result in greater reflectance discontinuities and residual cloud cover in the resulting composites. Given Ghana's persistent cloudiness, such artifacts were present in a number of our PlanetScope composites. However, these were not large enough to have an appreciable impact on the resulting maps, as the mapping algorithms appeared to be relatively insensitive to these anomalies and any discontinuities along tile boundaries.

@@

## Conclusion
This work demonstrates a proof of concept for developing high resolution, annual maps of field boundaries in smallholder-dominated croplands at national to regional scales.  The approach we used to develop these maps includes a novel procedure for compositing daily PlanetScope imagery, and follows recommended best practices for training and assessing machine learning models [@ElmesAccountingtrainingdata2020]. Using PlanetScope data enabled us to make a country-wide, high-resolution, two-season catalog of imagery for a single year, even over areas with frequent cloud cover. Methods to assess labeller accuracy and to create consensus labels helped to  minimize training label errors, which in turn substantially improved the accuracy of the mapping model. Model performance was further enhanced by using an active learning framework, which selects the most informative training sample. This mapping approach can be readily updated to integrate improvements, such as newer machine learning models.

The resulting maps provide valuable information on Ghana's agricultural systems, including an updated estimate of cropped area, and new data on the characteristics of Ghana's cropping systems, such as the sizes and numbers of fields. Beyond the  information about field characteristics, field boundary maps can help improve remote estimation of crop areas and yield [e.g. @EstesProjectedclimateimpacts2013], and provide deeper insights into important socioeconomic aspects of agricultural systems, such as the relationships between agricultural productivity and farm size [@CarlettoFactartifactimpact2013; @desiereLandProductivityPlot2018; @federRelationFarmSize1985]. Such maps will be important for understanding the rapid agricultural change that is currently occurring in Africa.

# Data availability and usage
The maps presented here are a version 1 product that is freely available to use, along with its underlying code (see SI). In their current form, they may be useful for a variety of research applications. For example, analyzing the distributions of values in the probability maps may provide additional insight into the relative extents of active versus fallow croplands [@Tongforgottenlanduse2020]. However, use of these data for inventory estimates, to develop other map products, or to guide decision-making should be made with caution and account for the reported errors [@OlofssonGoodpracticesestimating2014; @StehmanKeyissuesrigorous2019; @Esteslargeareaspatiallycontinuous2018].
